signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-19 paper.tex
fixing hsmm diagram

(1,-2.8) -- (12,-2.8) node [branch2, midway, yshift=-1.5cm,color=black] {\textbf{Observations, $\sum_{i=1}^k d_i = T$}};

>>>>

\draw [color=red!30!black!50, line width=1.5mm, decorate,decoration={brace,amplitude=15pt,mirror,raise=10pt},yshift=-10pt]
(1,-2.6) -- (12,-2.6) node [branch2, midway, yshift=-1.3cm,color=black] {\textbf{Observations, $\sum_{i=1}^k d_i = T$}};
